Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution

### 2021-06-28 Paper/Submission_new/Main_Document-Latex.tex
28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Updat

We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above. We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from the established European trait dataset, namely size, feeding mode, locomotion, oviposition, respiration, and voltinism.
We compared the results of the original study’s RDA with the results of the RDA from the harmonised grouping features. Specifically, trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electrical conductivity gradient. We compared the species scores obtained from the RDA (i.e., the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots). Following the original study, we used the Mahalanobis distance measure and identified traits associated with higher or lower salinity based on their distance to the ordination axis median. We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity. Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
% Add change in functional diversity

@@

>>>>

We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above. We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from the established European trait dataset, namely size, feeding mode, locomotion, oviposition, respiration, and voltinism.
We compared the results of the original study’s RDA with the results of the RDA from the harmonised grouping features. Specifically, trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electrical conductivity gradient. We compared the species scores obtained from the RDA (i.e., the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots). Following the original study, we used the Mahalanobis distance measure and identified traits associated with higher or lower salinity based on their distance to the ordination axis median. We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity. Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.

Finally, we assessed how functional diversity (FD) changed when harmonised and aggregated trait data are used. Harmonisation of grouping features reduces the number of traits per grouping feature and thus likely influences FD metrics, e.g. for the freshwaterecology.info database ten feeding mode traits were combined to six traits. We calculated functional richness (FRic), functional evenness (FEve), and functional divergence (FDiv) following \citet{villegerNewMultidimensionalFunctional2008a} with the traits from \citet{szocs_effects_2014}, harmonised grouping features from the European trait dataset, and with family-level aggregated trait values. For FEve and FDiv invertebrate abundance data were used from \citet{szocs_effects_2014}. To account for temporal autocorrelation (sampling was done over a time period of three years) we regressed each FD metric with year and extracted the residuals. The residuals of the original study were compared with the residuals of the harmonised and aggregated datasets through regression for each FD metric.
% R2!

@@

Calculating FD metrics for the original, harmonised (not aggregated), and aggregated datasets showed that the use of harmonised trait data results in similar FRic and FDiv values compared to the original dataset ($R2 = 0.96$ and $0.86$, respectively). Generally, aggregated trait data yielded lower, but moderate to good, correlations to the original for FRic and FDiv than the harmonised (Figure \ref{fig:FRic} and \ref{fig:FDiv}). 
By contrast, FEve calculated with harmonised and aggregated trait data seemed to substantially differ from the original dataset (all correlations below $< 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which had an $R2$ of 0.48 (Figure \ref{fig:FEve}).

% Evaluated by R2
